\cvsection[sidebars/page1sidebar]{Experience}

{\small
\cvevent{Quality Assurance Consultant}{DB}{2020 -- 2025}{Porto Alegre, Brasil (Remote)}
\begin{itemize}
    \item Designed and executed test plans, test cases, test cycles, and user journeys, ensuring full coverage of business requirements.
    \item Developed and maintained automated test frameworks using Java and JavaScript with Selenium, TestNG, Cypress, RestAssured and JUnit integrated with pipelines for continuous testing.
    \item Applied advanced QA methodologies, including risk-based testing, boundary value analysis, equivalence partitioning, data-driven testing, and session-based exploratory testing.
    \item Collaborated with cross-functional teams, including developers and data scientists, to validate predictive models, APIs, and complex workflows, integrating results into automated and manual tests.
    \item Managed test documentation, traceability matrices, and execution evidence to support regression cycles, audits, and compliance.
    \item Mentored interns and colleagues, bridging manual testing practices to automation, and created training materials and course reviews to improve QA knowledge across teams.
    \item Participated in Agile ceremonies (sprint planning, refinement, retrospectives) and organized tasks via Kanban in Jira or Azure Board to optimize workflow and test prioritization.
    \item Contributed to automation strategy, pipeline implementation, and code refactoring to improve efficiency, maintainability, and scalability of testing frameworks.
    
    \item \textbf{Seniority progression:}
    \begin{itemize}
        \item Promoted to \textbf{Plena} (mid-level) — 2020
        \item Promoted to \textbf{Senior} — 2023
    \end{itemize}
    
    \item Projects:
    \begin{itemize}
        \item \textbf{RENNER}
        \begin{itemize}
            \item Implemented frontend automation using Cypress to cover critical user journeys and regression suites, integrated into CI pipelines.
            \item Reviewed and validated predictive models developed by data scientists, creating test cases and acceptance criteria to ensure model reliability and API correctness.
            \item Founded the QA function within the squad where none existed before; established testing practices, pipelines and quality gates to improve early defect detection—highlighted positively for hiring teams.
            \item Acted as primary responder for all bugs, incidents and production faults, handling triage, fixes and root-cause analysis to reduce recurrence.
            \item Ensured quality across multiple environments and browsers, applying cross-browser testing, parameterized testing, and data management strategies.
        \end{itemize}
        \item \textbf{SICREDI}
        \begin{itemize}
            \item Sole QA for a critical bank risk system, owning end-to-end quality for both legacy and modern components.
            \item Maintained a legacy subsystem responsible for sending regulatory reports to BACEN (Central Bank of Brazil).
            \item Created and executed sequences of Oracle SQL queries for test data setup, verification and automated assertions; integrated these queries into CI-driven test suites.
            \item Coordinated across development, operations and compliance teams to validate data flows, interfaces and regulator submissions.
            \item Built regression and integration tests to reconcile legacy outputs with central records, reducing post-release defects and improving audit readiness.
        \end{itemize}
        \item \textbf{Internship mentor}
    \end{itemize}
    \item Tech stack:
    \begin{itemize}
        \item \textbf{Languages}: {\color{accent2}Java, Javascript, SQL}
        \item \textbf{CI/CD}: {\color{accent2}GitLab CI/CD, Azure Pipelines, Circle CI, GitHub Actions}
        \item \textbf{DataBase}: {\color{accent2}MongoDB, Oracle, MySQL, PostgreSQL}
        \item \textbf{Frameworks}: {\color{accent2}Selenium, Cypress, RestAssured, TestNG, Cucumber, JUnit}
        \item \textbf{API}: {\color{accent2}Postman, Swagger, Insomnia}
        \item \textbf{Board}: {\color{accent2}Jira, Azure Board, Trello}
    \end{itemize}
\end{itemize}

\cvevent{Quality Analyst Consultant}{GETNET/Compasso}{2019}{Porto Alegre, Brazil}
\begin{itemize}
    \item Test analyst in a squad responsible for chargebacks in the GETNET banking process.
    \item Automated backend testing with Postman and integrated executions into Azure Pipelines,
    \item Authored and executed detailed test scripts for both manual and automated pipelines using Azure Test Plans.
    \item Operated under SCRUM methodology with Azure Board for sprint and Kanban management.
    \item Tech stack:    
    \begin{itemize}
        \item \textbf{Languages}: {\color{accent2}Java, Javascript}
        \item \textbf{CI/CD}: {\color{accent2}GitLab CI/CD}
        \item \textbf{Frameworks}: {\color{accent2}Selenium, Cypress, TestNG, JUnit}
        \item \textbf{API}: {\color{accent2}Postman}
        \item \textbf{Board}: {\color{accent2}Azure Board}
    \end{itemize}
\end{itemize}

\cvevent{Dev FullStack}{Aceleradora Ágil/ThoughtWorks}{2019}{Porto Alegre, Brazil}
\begin{itemize}
    \item Contributed to the delivery of a complete software project from concept to deployment of the application Raizes.
    \item Worked in pair-programming rotations across all development stages: database design, backend (Java, Spring, Hibernate), frontend (JavaScript, HTML, CSS, SASS, Thymeleaf) and tests (Cypress, JUnit)
    \item Collaborated closely with the Product Owner and team members to clarify requirements and ensure alignment between development and testing
    \item Actively participated in Agile ceremonies, improving sprint delivery predictability.
    \item Tech stack:    
    \begin{itemize}
        \item \textbf{Languages}: {\color{accent2}Java, Javascript, SQL}
        \item \textbf{CI/CD}: {\color{accent2}Travis CI, Circle CI, Heroku}
        \item \textbf{DataBase}: {\color{accent2}MongoDB, PostgreSQL}
        \item \textbf{Frameworks}: {\color{accent2}Selenium, Cypress, TestNG, JUnit}
        \item \textbf{Board}: {\color{accent2}Trello}
    \end{itemize}
\end{itemize}

% ...existing code...
